---
title: "Creating a Zero Bin Histogram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{creating_zero_bin_histogram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(zeroBinHist)
library(dplyr)
library(lubridate)
library(janitor)
library(stringr)

```

Reading in the data:
``` {r}

raw_stock_price_data <- read.csv("~/zeroBinHist/vignettes/HistoricalData_1746910817326.csv")

daily_change <- raw_stock_price_data %>% 
  janitor::clean_names() %>% 
  mutate(date = mdy(date)
         , close = close_last %>% str_remove_all(fixed("$")) %>% as.numeric()) %>% 
  arrange(date) %>% 
  transmute(date, close, daily_percent_change = close/lag(close) - 1, year = year(date))

```

Use `bin_data_with_zero` to create zero binned data. This is done two ways, one partitioned by year and the other without a grouping column. This example uses the daily percent change in the closing price for COF from 2015-2023.

``` {r}

binned_data <- bin_data_with_zero(daily_change, value_col = "daily_percent_change")
yearly_binned_data <- bin_data_with_zero(daily_change, value_col = "daily_percent_change", group_col = "year")

head(yearly_binned_data)

```

Use `plot_zero_bin_histogram` and the output from `bin_data_with_zero` to create a baic histogram with a zero bin.

``` {r}
plot <- plot_zero_bin_histogram(binned_data, counter = 0.005, x_format = percent_format(0.01))+
  theme(axis.title.x = element_blank())

print(plot)

```
When overlaying multiple distributions, use `yearly_binned_data_to_plot` to add color and a legend.

``` {r}

yearly_binned_data_to_plot <- yearly_binned_data %>% 
  filter(year %in% c(2015, 2023)) %>% 
  mutate(year = year %>% as.character())

plot_yearly <- plot_zero_bin_histogram(yearly_binned_data_to_plot, group_col = "year"
                                       , counter = 0.005, x_format = percent_format(0.01), drop_line = T)

plot_yearly_with_legend <- customize_zero_bin_legend(plot_yearly, yearly_binned_data_to_plot, group_col = "year"
                                                                  , fill_colors = c("2015" = "darkred", "2023" = "navy")) + 
  theme(legend.position="bottom") +
  theme(legend.title=element_blank(),
        axis.title.x = element_blank())+
  theme_bw()

print(plot_yearly_with_legend)

```
